---
title       : Central Limit Theorem
subtitle    : 
author      : José Rodrigo Cervantes
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---
## Central Limit Theorem

Let $\{ X_{1} , \cdots , X_{n} \}$ be a sequence of I.I.D random variables of size $n$ drawn from distributions of expected values given by $\mu$ and finite variance given by $\sigma^2$. 

Suppose we are interested in the sample average
$$ \bar X_{n} = \frac{X_{1} + \cdots + X_{n}}{n} $$
of these random variables. 

The CLT states that as $n$ gets larger, the distribution of $\bar X_n$ is close to the normal distribution with mean $\mu$ and variance $\frac{\sigma^2}{n}$.

---
## Simulation

We fixed a few basic settings to be used during this analysis. 
```{r echo=TRUE, cache=FALSE, message=FALSE}
## setwd("~/.....)    # set the directory
library(ggplot2)      # to be able to graph
set.seed(0)           # to be able to reproduce
```

The following code shows how to build 1000 simulations of averages of 40 exponentials with $\lambda = 0.2$.

```{r}
# Number of simulations
numsim = 1000                                                
# Create the simulations
sample = NULL                                                
for (i in 1 : numsim) sample = c(sample, mean(rexp(40,0.2))) 
# Create a dataframe (ggplot)
sample<-as.data.frame(sample)                                
```

---
## Mean and Standard deviation

Now, we calculate the sample mean and sample variance:
```{r}
mean(sample$sample)
var(sample$sample)
```
A consequence of the CLT is that the mean and variance of the random variable given by the average are approximated by

$$\mu = 1/\lambda = 1/0.2 = 5\quad\text{and}\quad\sigma^2/n = 25/40 = 0.625$$

respectively.

---
```{r, tidy=FALSE,  echo=FALSE}
g <- ggplot(sample,aes(sample))     # Enter the database to be graph
g <- g + geom_histogram(binwidth=.1,aes( y=..density..))  # Type of graph / histogram
g <- g + stat_function(fun = dnorm,args = list(mean=mean(sample$sample), 
                                               sd = sd(sample$sample)), color = "green")
g <- g + labs(title="Normal Distribution Approximation",x="Sample",y="Frequency")
g
```

In the following website there is an application where you can move a few parameters of the previous example: [app](http://romath.shinyapps.io/DevelopingDataProducts).





